Gender and international diversity improves equity in peer review: R Notebook, August 2018

### 2018-08-18 eLife_Analysis_and_Figures.Rmd
Updated figures, added .png format

fig2 <- grid.arrange(p1, p2, ncol = 2)
ggsave("figures/main/fig_2.tiff", plot = fig2, height = 4, width = 7)

@@

fig3 <- grid.arrange(p1, p2)
ggsave("figures/main/fig_3.tiff", plot = fig3, height = 5, width = 7)
```

@@

fig4
ggsave("figures/main/fig_4.tiff", plot = fig4, height = 5, width = 7)
```

@@

fig5
ggsave("figures/main/fig_5.tiff", plot = fig5, height = 5, width = 7)
```

@@

fig6 <- grid.arrange(p1, p2)
ggsave("figures/main/fig_6.tiff", plot = fig6, height = 6, width = 8)
```

@@

ggsave("figures/main/fig_7.tiff", plot = fig7, height = 4, width = 7)
```

@@

fig_SI.1
ggsave("figures/supp/fig_SI1.tiff", plot = fig_SI.1, height = 4, width = 7)
```

@@

fig_SI.2 <- elife %>%
  filter(initial_decision_made) %>%
  gather(author_key, value = gender, ca_gender, la_gender, fa_gender) %>%
  filter(gender %in% c('M', 'F')) %>%
  group_by(author_key) %>%
  mutate(
    # if not ocnsidering the corr. author, then the count is all full submissions, ie: for when a submission ia made
    total_papers = ifelse(author_key == "ca_gender", n(), sum(has_full_submission))
    )%>%
  group_by(author_key, gender) %>%
  summarize(
        paper_count = n(),
        accept_count = sum(accepted == TRUE, na.rm = T),
        encourage_count = sum(encouraged == TRUE),
        encourage_rate = ifelse(author_key[1] == "ca_gender", encourage_count / n(), NA),
        # this accept rate is the number of accepted papers / number of initial + full submissions
        accept_rate = ifelse(author_key[1] == "ca_gender", accept_count / sum(!has_full_submission | full_decision_made, na.rm = T), NA),
        submit_rate = n() / total_papers[1],
        # this is the number of accepted papers divided by all papers 
        encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  ungroup() %>%
  gather(measure_key, value = measurement, submit_rate, encourage_rate, accept_rate, encourage_accept_rate) %>%
  left_join(sig_df, by = c("measure_key", "author_key")) %>%
  mutate(
    author_key = factor(author_key,
                        levels = c("ca_gender", "fa_gender", "la_gender"),
                        labels = c("ca_gender" = "Corresponding Author", "fa_gender" = "First Author", "la_gender" = "Last Author")
                        ),
    measure_key = factor(measure_key, 
                         labels = c("submit_rate" = "Submissions", "encourage_rate" = "Enc %", "accept_rate" = "Overall Acc %", "encourage_accept_rate" = "Accept %"),
                         levels = c("submit_rate", "encourage_rate", "accept_rate", "encourage_accept_rate")),
    gender = ifelse(gender == "F", "Female", "Male"),
    standard_error = 1.96 * sqrt( (measurement * (1 - measurement)) / paper_count),
    lower = measurement - standard_error,
    upper = measurement + standard_error
  ) %>%
  ggplot(aes(x = gender, y = measurement, color = factor(gender), shape = factor(gender), fill = factor(gender))) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  #geom_text(aes(y = 0.08, label = paper_count), size = 2.5, color = "black") +
  #geom_text(aes(x = gender, y = 0.1, label = round(measurement, 3) * 100 ), color = "black") +
  #facet_grid(measure_key ~ author_key) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black") +
  geom_text(aes(x = 1.5, y = 0.95, label = ifelse(measure_key == "Submissions", "", as.character(sig))), color = "black") +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.90, 1.1), yend = ifelse(sig != "N/A", 0.90, 1.1)), color = "black") +
  facet_grid(author_key ~ measure_key) +
  coord_cartesian(ylim = c(0, 1)) +
  theme_dakota() +
  guides(fill = F) +
  labs(
    x = "Gender of Author",
    y = "% accepted of full submissions"
  )

fig_SI.2
ggsave("figures/supp/fig_SI2.tiff", plot = fig_SI.2, height = 4, width = 7)
```

@@

fig_SI.3
ggsave("figures/supp/fig_SI2.tiff", plot = fig_SI.2, height = 4, width = 7)
```

@@

fig_SI.4 <- grid.arrange(p1, p2)
ggsave("figures/supp/fig_SI3.tiff", plot = fig_SI.3, height = 4, width = 7)
```

@@

fig_SI.5
ggsave("figures/supp/fig_SI5.tiff", plot = fig_SI.5, height = 4, width = 7)
```

@@

fig_SI.6
ggsave("figures/supp/fig_SI6.tiff", plot = fig_SI.6, height = 4, width = 7)
```

@@

fig_SI.7
ggsave("figures/supp/fig_SI7.tiff", plot = fig_SI.7, height = 4, width = 7)
```

>>>>

fig2 <- grid.arrange(p1, p2, ncol = 2)
ggsave("figures/main/fig_2.tiff", plot = fig2, height = 4, width = 7)
ggsave("figures/main/fig_2.png", plot = fig2, height = 4, width = 7)

@@

fig3 <- grid.arrange(p1, p2)
ggsave("figures/main/fig_3.tiff", plot = fig3, height = 5, width = 7)
ggsave("figures/main/fig_3.png", plot = fig3, height = 5, width = 7)
```

@@

fig4
ggsave("figures/main/fig_4.tiff", plot = fig4, height = 5, width = 7)
ggsave("figures/main/fig_4.png", plot = fig4, height = 5, width = 7)
```

@@

fig5
ggsave("figures/main/fig_5.tiff", plot = fig5, height = 5, width = 7)
ggsave("figures/main/fig_5.png", plot = fig5, height = 5, width = 7)
```

@@

fig6 <- grid.arrange(p1, p2)
ggsave("figures/main/fig_6.tiff", plot = fig6, height = 6, width = 8)
ggsave("figures/main/fig_6.png", plot = fig6, height = 6, width = 8)
```

@@

ggsave("figures/main/fig_7.tiff", plot = fig7, height = 4, width = 7)
ggsave("figures/main/fig_7.png", plot = fig7, height = 4, width = 7)
```

@@

fig_SI.1
ggsave("figures/supp/fig_SI1.tiff", plot = fig_SI.1, height = 4, width = 7)
ggsave("figures/supp/fig_SI1.png", plot = fig_SI.1, height = 4, width = 7)
```

@@

fig_SI.2 <- elife %>%
  filter(initial_decision_made) %>%
  gather(author_key, value = gender, ca_gender, la_gender, fa_gender) %>%
  filter(gender %in% c('M', 'F')) %>%
  group_by(author_key) %>%
  mutate(
    # if not ocnsidering the corr. author, then the count is all full submissions, ie: for when a submission ia made
    total_papers = ifelse(author_key == "ca_gender", n(), sum(has_full_submission))
    )%>%
  group_by(author_key, gender) %>%
  summarize(
        paper_count = n(),
        accept_count = sum(accepted == TRUE, na.rm = T),
        encourage_count = sum(encouraged == TRUE),
        encourage_rate = ifelse(author_key[1] == "ca_gender", encourage_count / n(), NA),
        # this accept rate is the number of accepted papers / number of initial + full submissions
        accept_rate = ifelse(author_key[1] == "ca_gender", accept_count / sum(!has_full_submission | full_decision_made, na.rm = T), NA),
        submit_rate = n() / total_papers[1],
        # this is the number of accepted papers divided by all papers 
        encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  ungroup() %>%
  gather(measure_key, value = measurement, submit_rate, encourage_rate, accept_rate, encourage_accept_rate) %>%
  left_join(sig_df, by = c("measure_key", "author_key")) %>%
  mutate(
    author_key = factor(author_key,
                        levels = c("ca_gender", "fa_gender", "la_gender"),
                        labels = c("ca_gender" = "Corr. Author", "fa_gender" = "First Author", "la_gender" = "Last Author")
                        ),
    measure_key = factor(measure_key, 
                         labels = c("submit_rate" = "Submissions", "encourage_rate" = "Enc %", "accept_rate" = "Overall Acc %", "encourage_accept_rate" = "Accept %"),
                         levels = c("submit_rate", "encourage_rate", "accept_rate", "encourage_accept_rate")),
    gender = ifelse(gender == "F", "Female", "Male"),
    standard_error = 1.96 * sqrt( (measurement * (1 - measurement)) / paper_count),
    lower = measurement - standard_error,
    upper = measurement + standard_error
  ) %>%
  ggplot(aes(x = gender, y = measurement, color = factor(gender), shape = factor(gender), fill = factor(gender))) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  #geom_text(aes(y = 0.08, label = paper_count), size = 2.5, color = "black") +
  #geom_text(aes(x = gender, y = 0.1, label = round(measurement, 3) * 100 ), color = "black") +
  #facet_grid(measure_key ~ author_key) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black") +
  geom_text(aes(x = 1.5, y = 0.95, label = ifelse(measure_key == "Submissions", "", as.character(sig))), color = "black") +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.90, 1.1), yend = ifelse(sig != "N/A", 0.90, 1.1)), color = "black") +
  facet_grid(author_key ~ measure_key) +
  coord_cartesian(ylim = c(0, 1)) +
  theme_dakota() +
  guides(fill = F) +
  labs(
    x = "Gender of Author",
    y = "% accepted of full submissions"
  )

fig_SI.2
ggsave("figures/supp/fig_SI2.tiff", plot = fig_SI.2, height = 4, width = 7)
ggsave("figures/supp/fig_SI2.png", plot = fig_SI.2, height = 4, width = 7)
```

@@

fig_SI.3
ggsave("figures/supp/fig_SI3.tiff", plot = fig_SI.3, height = 4, width = 7)
ggsave("figures/supp/fig_SI3.png", plot = fig_SI.3, height = 4, width = 7)
```

@@

fig_SI.4 <- grid.arrange(p1, p2)
ggsave("figures/supp/fig_SI4.tiff", plot = fig_SI.4, height = 4, width = 7)
ggsave("figures/supp/fig_SI4.png", plot = fig_SI.4, height = 4, width = 7)
```

@@

fig_SI.5
ggsave("figures/supp/fig_SI5.tiff", plot = fig_SI.5, height = 4, width = 7)
ggsave("figures/supp/fig_SI5.png", plot = fig_SI.5, height = 4, width = 7)
```

@@

fig_SI.6
ggsave("figures/supp/fig_SI6.tiff", plot = fig_SI.6, height = 4, width = 7)
ggsave("figures/supp/fig_SI6.png", plot = fig_SI.6, height = 4, width = 7)
```

@@

fig_SI.7
ggsave("figures/supp/fig_SI7.tiff", plot = fig_SI.7, height = 4, width = 7)
ggsave("figures/supp/fig_SI7.png", plot = fig_SI.7, height = 4, width = 7)
```
